--- 
title: |
  | My First Steps in Neuronal Networks
  | (Beginners Guide)
author: "Axel Roth"
date: "`r Sys.Date()`"
description: This GitBook should provide an slide insight into my own learning process of coding Neuronal Networks (NN). Additionaly its a good chance for me to learn how to write a GitBook.
documentclass: book
github-repo: https://github.com/AxelCode-R/GitBook
link-citations: yes
bibliography:
- book.bib
- packages.bib
site: bookdown::bookdown_site
biblio-style: apalike
header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

# About
## Me
Hello, my name is Axel Roth and im studding math at a master degree in germany and working half-time in the finance field as something between a data-analyst and a full stack developer. I already got a lot of experience in coding with R and all its features, but i never wrote a line of code in python and i never touched Neuronal Networks bevor. So Why do i want to write a beginners guide in the field of Neuronal Networks in python?  
Its simple, at the moment im having a lecture in that we learn how to program a Neuronal Network from scratch with basic packages from python and i want to share my experience. Additionally i learned all i know from free sources of the internet and thats why i want to give something back. Furthermore its a good use-case to write my first things in english and test the fancy Bookdown and GitBook features. 

## The Book
This Book will be more or the less the documentation of my lecture in that we learn to program a simple Perceptron (the simplest Neuronal Network) and then we will continue with a multi layer Perceptron and finish with a slight insight into decision trees. On this journey, we will test the Neuronal Network in different examples that are easy to reproduce. Because these are my first steps in this field, i need to appolagice for my terrible spelling and cant guarantee you the best quality, but maybe this is the best way to educate and attract unexperienced readers to have a look into this field.  

## How it works
Im coding this book in the IDE R-Studio with the framework of Bookdown and embed python code that is made possible by the reticulate package. This is the reason, why i need to load the python interpreter in the following R-chunk:
```{r, warning=FALSE}
library(reticulate)
Sys.setenv(RETICULATE_PYTHON = "D:\\WinPython2\\WPy64-3950\\python-3.9.5.amd64\\")
```
Additionaly im using a fully portable version of R-Studio, R and python. Its nice to have if you want to switch for example between university PCs and your own. R-Studio supports it and python can be downloaded via WinPython to be fully portable. All the Neural Network pictures are handmade by me with draw.io, its a free to use website. If you are new to python and never used R i would recommend to use jupyter lab or PyCharm.

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = "hold"
)
options(scipen=999)
```
```{python, include=FALSE}
import pandas as pd
import numpy as np
pd.set_option('display.max_rows', 500)
pd.set_option('display.max_columns', 500)
pd.set_option('display.width', 1000)
np.set_printoptions(suppress=True)
```


 
