--- 
title: |
  | My First Steps in Neuronal Networks
  | (Beginners Guide)
author: "Axel Roth"
date: "`r Sys.Date()`"
description: This GitBook should provide an slide insight into my own learning process of coding Neuronal Networks (NN). Additionaly its a good chance for me to learn how to write a GitBook.
documentclass: book
github-repo: https://github.com/AxelCode-R/GitBook
link-citations: yes
bibliography:
- book.bib
- packages.bib
site: bookdown::bookdown_site
biblio-style: apalike
header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

# About
## Me
Hello, my name is Axel Roth, and I'm pursuing a master's degree in mathematics in Germany while working part-time in finance as something between a data analyst and a full stack developer. I have a lot of experience with R and all of its features, but I have never written a line of Python code or worked with Neuronal Networks before. So, why am I writing a Python Beginner's Guide to Neuronal Networks in the first place? It's simple. I'm currently attending a lecture in which we're learning how to program a Neuronal Network from scratch using basic Python packages, and I'd like to share my experience. Furthermore, I learned everything I know from free internet sources, which is why I want to give something back. It's also a good use-case for me to write my first things in English.


## The Book
This book will essentially be a transcript of my lecture, in which we will learn to program a simple Perceptron (the most basic Neuronal Network), then progress to a multilayer Perceptron, and finally to a brief overview of decision trees. On this journey, we'll put the Neuronal Network to the test in a variety of scenarios that are simple to replicate. Because these are my first steps in this field, I apologize for my terrible spelling and cannot guarantee the highest quality, but this may be the best way to educate and attract uninitiated readers to take a look.


## How it works
I'm writing this book in the R-Studio IDE, using the Bookdown framework, and using the reticulate package to embed python code. This is why I need to load the Python interpreter in the R-chunk below:
```{r, warning=FALSE}
library(reticulate)
Sys.setenv(RETICULATE_PYTHON = "D:\\WinPython2\\WPy64-3950\\python-3.9.5.amd64\\")
```
In addition, I use R-Studio, R, and Python in a portable manner. It comes in handy when you need to switch between university and home computers, for example. Python can be downloaded through WinPython to be fully portable, and R-Studio supports it. I created all of the Neural Network images using the free website draw.io and im using QuillBot to compensate for my poor spelling skills. I would recommend jupyter lab or PyCharm if you are new to Python and have never used R.

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = "hold"
)
options(scipen=999)
```
```{python, include=FALSE}
import pandas as pd
import numpy as np
pd.set_option('display.max_rows', 500)
pd.set_option('display.max_columns', 500)
pd.set_option('display.width', 1000)
np.set_printoptions(suppress=True)
```


 
